Leveraging Diversity to Find Bugs\\ in JavaScript Engines

### 2018-08-06 paper/paper.tex
fix table IV
fix table nofuzz
merging
merge
update table

\begin{table}[t]
  \centering
  \caption{\label{tab:test-suites}Test Suites. The sections of the
    table show, respectively, the TC-39 conformance test suite, suites
    from engines we analyzed, and suites from other engines.}
  \begin{tabular}{ccr}
    \toprule
    Name & Source & \# JS files \\
    \midrule
    TC-39 (Test262) & \cite{ecma262-conformance-suite} & 31,276 \\
    \midrule
    Mozilla & \cite{mozilla} & 2,633 \\
    \veight{} & \cite{v8} & 74 \\
    \jsc{} & \cite{webkit} & 1,031 \\
    \midrule    
    Duktape & \cite{duktape} & 1,195 \\ 
    JerryScript & \cite{jerryscript} & 1,950 \\
    JSI & \cite{jsi} & 98 \\
    Tiny-js & \cite{tinyjs} & 48 \\    
    % Chakra & \cite{chakracore} & 2632 \\
    \midrule
     &  & \totalTestFiles{} \\
   \bottomrule     
  \end{tabular}
\end{table}

@@

\begin{table}[h]
  \centering
  \caption{\label{tab:cross-testing}Number of failures observed exchanging
  test suites.}
  \begin{tabular}{crrrr}
    \toprule
    test suite\textbackslash{}engine & \jsc{} & \veight{} & \smonkey{} & \chakra{}\\
    \midrule
    \Fix{Versions (01.08)} & 234485 & 7.0.126 & 62.0b13 & 1.10.1 \\
    \midrule
    \jsc{} & - & 1 & 97 & 147   \\
    \veight{} & 29 & - & 0 & 0  \\
%    \chakra{} & - & - & - & -  \\
    \smonkey{} & 563 & 108 & 0 & 298   \\
    Duktape & 165 & 7 & 129 & 12   \\
    JerryScript & 26 & 21 & 22 & 23   \\
    JSI & 21 & 0 & 0 & 0   \\
    Tiny-js & 0 & 0 & 0 & 0  \\
    \bottomrule 
  \end{tabular}
\end{table}

>>>>

\begin{table}[t]
  \centering
  \caption{\label{tab:test-suites}Test Suites. The sections of the
    table show, respectively, the TC-39 conformance test suite, suites
    from engines we analyzed, and suites from other engines.}
  \begin{tabular}{ccr}
    \toprule
    Name & Source & \# JS files \\
    \midrule
    TC-39 (Test262) & \cite{ecma262-conformance-suite} & 31,276 \\
    \midrule
    \jsc{} & \cite{webkit} & 1,021 \\
    \smonkey\ & \cite{mozilla} & 2,116 \\
    \veight{} & \cite{v8} & 57 \\
    \midrule    
    Duktape & \cite{duktape} & 921 \\ 
    JerryScript & \cite{jerryscript} & 1,878 \\
    JSI & \cite{jsi} & 63 \\
    Tiny-js & \cite{tinyjs} & 37 \\    
    % Chakra & \cite{chakracore} & 2632 \\
    \midrule
     &  & \totalTestFiles{} \\
   \bottomrule     
  \end{tabular}
\end{table}

@@

\begin{table}[h]
  \centering
  \caption{\label{tab:cross-testing}Number of failures observed exchanging
  test suites.}
  \begin{tabular}{crrrr}
    \toprule
    test suite\textbackslash{}engine & \jsc{} & \veight{} & \smonkey{} & \chakra{}\\
    \midrule
    % \Fix{Versions (03.08)} & 234555 & 7.0.158 & 62.0b14 & 1.10.1 \\
    \Comment{
      Lembrar dos testes que os testes da propria engine falham:
      V8 0 
      JSC 6 
      Spidermonkey 58
    }
    \jsc{} & - & 9 & 10 & 58   \\
    \veight{} & 29 & - & 0 & 0  \\
%    \chakra{} & - & - & - & -  \\
    \smonkey{} & 218 & 107 & - & 279 \\
    Duktape & 0 & 4 & 4 & 1   \\
    JerryScript & 23 & 25 & 22 & 23   \\
    JSI & 0 & 0 & 0 & 0   \\
    Tiny-js & 0 & 0 & 0 & 0  \\
    \bottomrule 
  \end{tabular}
\end{table}
